\documentclass{article}

\usepackage{fancyhdr}
\usepackage{extramarks}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage[plain]{algorithm}
\usepackage{algpseudocode}
\usepackage{nameref}
\usepackage{cite}

\usetikzlibrary{automata,positioning}


\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1}

\pagestyle{fancy}
\chead{\hmwkTitle}
\lhead{\hmwkAuthorName}
\rhead{\hmwkClass}
\cfoot{\thepage}

\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}
\newcommand{\sur}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\sous}[1]{\ensuremath{_{\textrm{#1}}}}

\setlength\parindent{0pt}

%c
% Create Problem Sections
%

\newtheorem{lemma}{Lemma}[section]
\newtheorem{exercise}{Exercise}
%
% Homework Details
%   - Title
%   - Due date
%   - Class
%   - Section/Time
%   - Instructor
%   - Author
%

\newcommand{\hmwkTitle}{Homework 3}
\newcommand{\hmwkDueDate}{October 17th, 2018}
\newcommand{\hmwkClass}{Math 225A Differential Topology}
\newcommand{\hmwkClassInstructor}{Professor Peter Petersen}
\newcommand{\hmwkAuthorName}{\textbf{Anish Chedalavada}}

%
% Title Page
%

\title{
    \vspace{2in}
    \textmd{\textbf{\hmwkClass:\ \hmwkTitle}}\\
    \vspace{0.1in}
    \textmd{\hmwkDueDate} \\
    \vspace{0.2in}\large{\textit{\hmwkClassInstructor\  }}
    \vspace{2in}
}

\author{\hmwkAuthorName}
\date{}


\begin{document}

\maketitle

\pagebreak

\begin{exercise}
Show that if $f: X \to Y$ is a submersion then $f$ maps open sets to open sets.
  \end{exercise}

  \begin{proof}
    By the local submersion theorem, we have that $f$ is locally equivalent to the canonical submersion for $x \in X$,$y\in Y$ s.t. $f(x) = y$ is a submersion. Let $U \subset X$ be an open set containing $x \in X$. Without loss of generality, we may select a neighborhood $x \in N(x)$ with local coordinates for $N(x), f(N(x))$ fulfilling the local submersion theorem, and shrink $N(x)$ s.t. $N(x) \subset U$. The product topology on $R^{n}$ for $N(x)$ diffeomorphic to $V \subset R^{n}$ yields that the projection of any open set onto any subspace yields an open set, i.e. that the projection map is an open map. As $f$ is equivalent to the canonical submersion for $N(x)$, we have that the image of $f$ on $N(x)$ must be an open set in $Y$. Thus, for any arbitrary $x \in f(U)$ we have a neighborhood $f(x) \in f(N(x)) \subset f(U)$ as constructed above, yielding the claim.
  \end{proof}

  \begin{exercise}
    Show that every submersion of a compact space into a connected space is surjective. In particular, show that there exist no submersions of compact manifolds into Euclidean spaces.
  \end{exercise}

  \begin{proof}
    From the previous exercise, we have that the image of an open set under a submersion is an open set. Thus, for $f:X \to Y$ with $X$ compact, $Y$ connected, we have that the image $f(X)$ must be open as $X \subset X$ open. However, $X$ is compact, $f$ is continuous, and thus $f(X)$ must be closed. As $Y$ is connected, this implies the only clopen set is $Y$ itself, and thus $f(X) = Y$. In particular, we have that as Euclidean space is connected and not compact, there are no continuous surjections from a compact space to all of Euclidean space and therefore no submersions.
  \end{proof}

  
\end{document}